Recruiting Chapter

### 2020-11-30 manuscript.Rmd
ugh

```{r, fig.width=3.5, fig.height=3, echo = FALSE, message = FALSE}
plot_characteristic <- function(df, type, characteristics) {
  sub_df <- df %>% select(University, characteristics) %>%
    gather(key, value, characteristics) %>%
    mutate(value = parse_number(value))

  # colors <- sub_df$color[order(sub_df$University)]
  univ_order <- (df %>% arrange(desc(Cluster), University))$University
  #univ_order <- (df %>% arrange(desc(Cluster), Type, as.numeric(Rank), University))$University
  sub_df$University <- factor(sub_df$University, levels = rev(univ_order))

  ggplot(sub_df, aes(fill = key, y = value, x = University)) + 
    geom_bar(stat='identity', position = position_fill(reverse = TRUE)) +
    ggtitle('Title') +
    xlab('') + ylab('') +
    labs(fill = type) +
    scale_y_continuous(labels = scales::percent, expand = c(0, 0, 0.05, 0)) +
    theme(legend.position = 'top',
          legend.title = element_text(size = 6, face = 'bold'),
          legend.text = element_text(size = 6),
          legend.margin = margin(0, 0, 0, 0),
          legend.box.margin = margin(0, 0, -5, -30),
          legend.key.size = unit(0.3, 'cm'),
          panel.background = element_blank(),
          axis.ticks.y = element_blank(),
          # axis.text.y = element_text(color = rep(c('red', 'green', 'blue', 'yellow', 'black'), 5)),
          text = element_text(size = 8),
          plot.title = element_text(color = 'white')) +
    coord_flip()
}

@@

  a <- plot_characteristic(ego_df, 'Region', c('Northeast', 'Midwest', 'South', 'West'))
  b <- plot_characteristic(ego_df, 'Religion', c('Catholic', 'Christian', 'Nonsect', 'Other'))
  c <- plot_characteristic(ego_df, '% Black/Latinx/Native', c('c1_lt10', 'c2_10to25', 'c3_25to50', 'c4_50+'))
  d <- plot_characteristic(ego_df, 'Ranking', c('c1_top200', 'c2_A+', 'c3_A', 'c4_ltA'))

>>>>

```{r, fig.width=3.5, fig.height=3, echo = FALSE, message = FALSE}
#df <-readRDS(file.path('.', 'assets', 'tables', str_c('table_ego_', 'privu', '.RDS')))
#df %>% glimpse()

plot_characteristic <- function(df, type, characteristics) {
  sub_df <- df %>% select(univ_name, characteristics) %>%
    gather(key, value, characteristics) %>%
    mutate(value = parse_number(value))

  # colors <- sub_df$color[order(sub_df$University)]
  univ_order <- (df %>% arrange(desc(cluster), univ_name))$univ_name
  #univ_order <- (df %>% arrange(desc(Cluster), Type, as.numeric(Rank), University))$University
  sub_df$univ_name <- factor(sub_df$univ_name, levels = rev(univ_order))
  #sub_df$univ_name

  ggplot(sub_df, aes(fill = key, y = value, x = univ_name)) + 
    geom_bar(stat='identity', position = position_fill(reverse = TRUE)) +
    ggtitle('Title') +
    xlab('') + ylab('') +
    labs(fill = type) +
    scale_y_continuous(labels = scales::percent, expand = c(0, 0, 0.05, 0)) +
    theme(legend.position = 'top',
          legend.title = element_text(size = 6, face = 'bold'),
          legend.text = element_text(size = 6),
          legend.margin = margin(0, 0, 0, 0),
          legend.box.margin = margin(0, 0, -5, -30),
          legend.key.size = unit(0.3, 'cm'),
          panel.background = element_blank(),
          axis.ticks.y = element_blank(),
          # axis.text.y = element_text(color = rep(c('red', 'green', 'blue', 'yellow', 'black'), 5)),
          text = element_text(size = 8),
          plot.title = element_text(color = 'white')) +
    coord_flip()
}

@@

  a <- plot_characteristic(ego_df, 'Region', c('northeast', 'midwest', 'south', 'west'))
  b <- plot_characteristic(ego_df, 'Religion', c('catholic', 'christian', 'nonsectarian', 'other'))
  c <- plot_characteristic(ego_df, '% Black/Latinx/Native', c('c1_lt10', 'c2_10to25', 'c3_25to50', 'c4_50+'))
  d <- plot_characteristic(ego_df, 'Ranking', c('c1_top200', 'c2_A+', 'c3_A', 'c4_ltA'))
